---
title: "TO628 Final Project Analytical Avengers"
author: "Group 4: Analytical Avengers"
date: "2023-04-04"
output: 
  html_document:
    toc : true
    toc_float : true
    toc_depth : 4
    number_sections : false
    code_folding: hide
    theme: spacelab
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#### Link to GitHub: https://github.com/rachaelfriedman/-to628-finalproject.git

# Project Proposal
#### Group: Analytical Avengers 
Patrick Burden, Rachael Friedman, Hardik Mehta, Benjamin Nahrstadt, Michael O’Brien 

We are using a data set called CBB which is college basketball regular season data.
We are trying to answer two questions. The first business question we are trying to answer is “Will a team make it to March Madness”. The second question is “If a team makes it to March Madness will a team make it past the second round”.



# Read the data

```{r}
marchmad <- read.csv("cbb.csv")
str(marchmad)
summary(marchmad)
```
# Clean the Data

Preliminary Data Exploration and Cleaning Details:
For cleaning the data, we removed team names and year because these variables would not be significant to predicting our result. 
We also created a calculated field to create a ratio between the number of wins and the number of games played by each team. 
We also factorized conference, post season, and seed variables.
We also created a new binary data field that identifies whether a team makes it to March Madness (where anytime Post Season not NA, this meant the team made it to March Madness, “1”) 


```{r}
marchmad$TEAM <- NULL
marchmad$YEAR <- NULL
marchmad$CONF <- as.factor(marchmad$CONF)
marchmad$WIN_PERC <-  (marchmad$W / marchmad$G)
marchmad$W <- NULL
marchmad$POSTSEASON <- as.factor(marchmad$POSTSEASON)
marchmad$QUALIFIED <- ifelse(is.na(marchmad$POSTSEASON), 0 , 1)
marchmad$SEED <- as.factor(marchmad$SEED)
str(marchmad)
summary(marchmad)
```


# Build and Run Model

Preliminary Regression Model Results:
We found that the number of games plays, adjusted offensive efficiency (ADJOE), adjusted defensive efficiency (ADJDE), the estimate of the team’s chance of winning against a typical D1 team (BARTHAG), free throw rate (FTR), wins above bubble (WAB), and win percentage (WIN_PERC) were all statistically significant coefficients.  


```{r}
mar_qual <- marchmad[, -c(1, 20, 21)]
str(mar_qual)
basemodel <- glm(QUALIFIED ~., data = mar_qual, family = "binomial")
summary(basemodel)

```

